Cognate beginnings to bilingual lexical acquisition

### 2023-06-28 manuscript/_appendix/_model-doe.qmd
Update PDF format

>>>>

A a robustness check, we fit a model similar to the one described in the main manuscript, but including lexical frequency and language degree of exposure as separate predictors, instead of the composite measure *Exposure*. Language degree of exposure (*DoE*) was included in interaction with *Age* and *Cognateness*, while lexical frequency (*Frequency*) was included as a main effect.

### 2023-06-28 manuscript/_appendix/_syllable-frequency.qmd
Update PDF format

@fig-top-syll-freq shows the top twenty most frequent syllables in Spanish. In both languages, most of the most frequent syllables followed a consonant-vowel (CV) structured. In Catalan, the most common nucleus in the most frequent syllables was /\textschwa/ (most likely due to vowel reduction in unstressed syllables), followed by /u/. In Spanish, the most common nucleus in the most frequent syllables were /a/ and /o/.

```{r fig-top-syll-freq}
#| label: fig-top-syll-freq
#| fig-cap: "Top 20 most frequent syllables"
#| fig-width: 8
#| fig-height: 3
#| out-width: 80%
#| echo: false
#| warning: false
#| message: false
syll |> 
    group_by(language) |> 
    top_n(20, freq_syll) |> 
    ggplot(aes(tidytext::reorder_within(syll, desc(freq_syll), language),
               freq_syll)) +
    facet_wrap(~ language,
               scales = "free_x",
               ncol = 1) +
    geom_col(colour = "white",
             fill = "grey70") +
    labs(x = "Syllable",
         y = "Relative frequency\n(counts per million)",
         colour = "Language",
         fill = "Language") +
    tidytext::scale_x_reordered() +
    scale_y_continuous(labels = \(x) format(x, big.mark = ",")) +
    theme(legend.position = "none",
          axis.title.x = element_blank(),
          axis.text.x = element_text(size = 10),
          panel.grid = element_blank())
```

To estimate the association between word-level syllabic frequency and cognateness while controlling for the number of syllables in the word, as words are expected to necessarily increase the syllabic frequency of the word), we fit a multilevel, Bayesian linear regression model with syllabic frequency (the sum of the syllabic frequency of the syllables in a word) as response variable, and the main effect of the number of syllables ($Syllables$) and $Cognateness$ (Levenshtein similarity between a word and its translation equivalent) as predictors. We added translation equivalent-level random effects for the intercept and the main effect of $Syllables$ (some translation pairs had a different number of syllables in each language). We used a Gaussian distribution to model syllabic frequency scores after standardising this variable and the predictors. We used a weakly informative prior for all parameters involved in the model (see @eq-model-syllables for a formal equation of this model and its prior).

>>>>

To estimate the association between word-level syllabic frequency and cognateness, while controlling for the number of syllables in the word, as words are expected to necessarily increase the syllabic frequency of the word), we fit a multilevel, Bayesian linear regression model with syllabic frequency (the sum of the syllabic frequency of the syllables in a word) as response variable, and the main effect of the number of syllables ($Syllables$) and $Cognateness$ (Levenshtein similarity between a word and its translation equivalent) as predictors. We added translation equivalent-level random effects for the intercept and the main effect of $Syllables$ (some translation pairs had a different number of syllables in each language). We used a Gaussian distribution to model syllabic frequency scores after standardising this variable and the predictors. We used a weakly informative prior for all parameters involved in the model (see @eq-model-syllables for a formal equation of this model and its prior).
